Figure 1f

### 2017-11-20 inst/3_prime_race/3_prime_race.Rmd
more of the previous commit 4

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

>>>>

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

### 2017-11-20 inst/coding_potential_cpat/coding_potential_cpat.Rmd
more of the previous commit 4

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

@@

url <- "figure1f_codingPotentialCPAT/results.txt"
cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
cpat

>>>>

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

url <- fileMap(type = "rds")["figure1f"][[1]]
cpat <-read_rds(url(file.path(dataUrl, url)))
cpat
